A Multiple-Set Overlapping-Domain Decomposed Monte Carlo Synthetic Acceleration Method for Linear Systems

### 2013-09-06 doc/dissertation/document/chapters/parallel_mc/parallel_mc.tex
adding parallel efficiency measures to sna paper
adding sna corrections through section 3

To parallelize the solution of Eq~(\ref{eq:mcsa_r3}), we apply the
MSOD Neumann-Ulam algorithm presented in the previous section. The
problem is potentially replicated with overlap and the Monte Carlo
procedure returns a correction vector, $\delta \ve{x}$, with the same
parallel decomposition as the input linear problem. As was the case
for generating the replications required for a multiple set
implementation, the explicit matrix and vector operations required for
the rest of an MCSA iteration occur only on the subset of processors
containing the primary set\footnote{For applications where resiliency
  is potentially of concern, the operations in Eqs~(\ref{eq:mcsa_r1}),
  (\ref{eq:mcsa_r2}), (\ref{eq:mcsa_r4}), and (\ref{eq:mcsa_r5}) may
  be replicated without significant penalty. Doing so my alleviate
  issues where any part of the linear problem or residual is disturbed
  as now there will be multiple copies of these data
  structures.}. Only the Monte Carlo data structures exist on the rest
of the processors in the problem as replication of the other
operations does not generate any more information that could be used
to accelerate the time to solution.

>>>>

To parallelize the solution of Eq~(\ref{eq:mcsa_r3}), we apply the
MSOD Neumann-Ulam algorithm presented in the previous section. The
problem is potentially replicated with overlap and the Monte Carlo
procedure returns a correction vector, $\delta \ve{x}$, with the same
parallel decomposition as the input linear problem. As was the case
for generating the replications required for a multiple set
implementation, the explicit matrix and vector operations required for
the rest of an MCSA iteration occur only on the subset of processors
containing the primary set\footnote{For applications where resiliency
  is potentially of concern, the linear problem and subsequently the
  operations in Eqs~(\ref{eq:mcsa_r1}), (\ref{eq:mcsa_r2}),
  (\ref{eq:mcsa_r4}), and (\ref{eq:mcsa_r5}) may be replicated with
  the penalty of broadcasting the data. Doing so may alleviate issues
  where any part of the linear problem or residual is disturbed as now
  there will be multiple copies of these data structures.}. Only the
Monte Carlo data structures exist on the rest of the processors in the
problem as replication of the other operations does not generate any
more information that could be used to accelerate the time to
solution.

### 2013-09-06 doc/sna2013/paper/slattery_evans_wilson.tex
adding sna corrections through section 3

where $W_c$ is a user defined cutoff. The random walk will then be
terminated after $m$ steps if $W_m < W_f$.

@@

The \textit{Fixed-Point Monte Carlo Synthetic Acceleration} method is
defined as:
\begin{subequations}
  \begin{gather}
    \label{eq:mcsa_1}
    \mathbf{r}^{k} = \mathbf{b} - \mathbf{A}\mathbf{x}^{k}\:,\\
    \label{eq:mcsa_2}
    \mathbf{x}^{k+1/2} = \mathbf{x}^k + \mathbf{r}^k\:,\\
    \label{eq:mcsa_3}
    \mathbf{r}^{k+1/2} = \mathbf{b} - \mathbf{A}\mathbf{x}^{k+1/2}\:,\\
    \label{eq:mcsa_4}
    \mathbf{A}\delta\mathbf{x}^{k+1/2} = \mathbf{r}^{k+1/2}\:,\\
    \label{eq:mcsa_5}
    \mathbf{x}^{k+1} = \mathbf{x}^{k+1/2} + \delta \mathbf{x}^{k+1/2}\:,
  \end{gather}
  \label{eq:mcsa}
\end{subequations}
where $\mathbf{r}$ is the residual vector, $\delta\mathbf{x}$ is the
Monte Carlo correction vector, and $k$ indicates the iteration
index. Here, a Neumann-Ulam Monte Carlo method is used to generate the
solution correction in Eq~(\ref{eq:mcsa_4}) using the residual as
source and Richardson's iteration in Eq~(\ref{eq:mcsa_2}) has been
rewritten as a residual correction. Using Monte Carlo in this way
achieves the same effect as Halton's method, decoupling its
convergence rate from the overall convergence rate of the method. For
the Neumann-Ulam method, a set number of random walk permutations is
specified to generate the correction at each MCSA iteration. Adding
more histories to the Neumann-Ulam sequence reduces the statistical
uncertainty in $\delta\mathbf{x}$ and further accelerates the
fixed-point iteration. In addition to the Monte Carlo solver
parameters dictating the number of histories and weight cutoff, the
outer MCSA iterations also have the following stopping criteria:
\begin{equation}
  ||\mathbf{r}||_\infty < \epsilon \ ||\mathbf{b}||_\infty\:,
  \label{eq:mcsa_stopping_criteria}
\end{equation}
where $\epsilon$ is a user-defined parameter.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Parallel Algorithms}
In this section devise a parallel algorithm for the Neumann-Ulam Monte
Carlo method based on the multiple-set overlapping-domain
decomposition algorithm and a parallel algorithm for the MCSA
iteration that leverages the parallel Monte Carlo algorithm and
general parallel matrix-vector operations.

\subsection{Parallel Neumann-Ulam Algorithm}
In the literature, current implementations of parallel Neumann-Ulam
methods have been limited to full domain replication with parallelism
exploited through individual histories
\cite{alexandrov_efficient_1998}. For high performance computing
environments, domain decomposition strategies have been identified as
important for Monte Carlo applications
\cite{brunner_comparison_2006,siegel_analysis_2012}. In a domain
decomposed Monte Carlo implementation, stochastic histories must be
communicated between domains as the simulation progresses and they
transition to locations outside of the local domain. In order to
implement domain decomposition strategy for Monte Carlo solvers in a
parallel environment, communication of these histories must occur
between compute nodes owning neighboring pieces of the global domain.

In the context of radiation transport, in 2009 Brunner and colleagues
provided a fully asynchronous domain decomposed parallel algorithm as
implemented in production implicit Monte Carlo codes
\cite{brunner_efficient_2009}. In their algorithm, a set of mutually
exclusive tasks enabled by the fully asynchronous communication
patterns are executed. For the Neumann-Ulam method, mutually
exclusivity permits all local operations to occur independently of
other processes in the system and their current state to achieve an
optimal overlap of work and communication. We will adapt their
algorithm and directly apply it to construct a parallel formulation of
the Neumann-Ulam method. Direct analogs can be derived from their
works by noting that the primary difference between solving a linear
transport system with Monte Carlo methods and traditional fixed source
Monte Carlo transport problems is the content of the Markov chains
that are generated.

Consider this communication pattern for the 9 subdomain example given
by Figure~\ref{fig:nearest_neighbor_comm}. In this pattern, each
boundary domain has two neighbors and the center domain four neighbors
with which they will communicate parallel histories and this
communication goes both ways as represented by the adjacent arrows in
the figure. For each set of neighbors, a non-blocking send and receive
is required with data buffers allocated with a user-defined size for
incoming and outgoing histories. This non-blocking structure is
critical to the performance of the algorithm in that it permits local
history transport to continue while new histories to transport are
being collected in the buffers. When a given process is ready to do
more work, it can check these data buffers for incoming histories
requiring further transport. In this way there is a maximum amount of
overlap between communication and transport of histories.

@@

Once the nearest-neighbor communication sequence has been completed
for all histories, the completion of transport sequence is
required. To stop transport, an asynchronous binary communication tree
as presented for the same 9 subdomain example in
Figure~\ref{fig:binary_comm_tree}. In this communication pattern, each
process has one parent process (except for the MASTER process 0) to
which it will non-blocking send the number of histories that
terminated their transport procedure by weight cutoff in the local
domain. Equivalently, each process has up to two child processes from
which it will receive their completed number of histories with a
non-blocking receive operation. Setting up a tree in this manner lets
the completed history tally be updated incrementally and funneled to
the root process. Because we are solving fixed source problems with
the Neumann-Ulam algorithm without any type of variance reduction that
may generate more histories that we started with, once the root
process completion sum tallies to the number of histories in the
source, transport is complete. Once this occurs, the root process
non-blocking sends the stop message to its children and each process
non-blocking receives a stop message from its parent as shown in
Figure~\ref{fig:binary_comm_tree}. The stop message is then propagated
up the tree in the same manner.
\begin{figure}[h!]
  \begin{center}
    \scalebox{0.6}{
      \input{binary_comm_tree.pdftex_t} }
  \end{center}
  \caption{Binary communication tree for coordinating the end of a
    parallel Neumann-Ulam solve. \textit{Each child process reports to
      its parents how many histories completed within its domain. When
      the root process sums all complete histories, it forwards the
      stop signal to its children which in turn forward the message up
      the tree. The subdomains are indexed by an integer.}}
  \label{fig:binary_comm_tree}
\end{figure}

\subsection{MSOD Algorithm}
At the 2010 SNA+MC meeting, Wagner and colleagues presented the
\textit{multiple-set overlapping-domain} (MSOD) decomposition method
for parallel Monte Carlo applications for full-core light water
reactor analysis \cite{wagner_hybrid_2010}. In their work, overlap
between adjacent domains in the decomposition was used to decrease the
number of particles leaving the local domain. In addition, Wagner
utilized a level of replication of the domain such that the domain was
only decomposed on $O(100)$ processors and if replicated $O(1,000)$
times achieves simulation on $O(100,000)$ processors, thus providing
spatial and particle parallelism. Each collection of processors that
constitutes a representation of the entire domain is referred to as a
set, and within a set overlap occurs among its sub-domains. The
original motivation was to decompose the domain in a way that it
remained in a physical cabinet in a large distributed machine, thus
reducing latency costs during communication.

To demonstrate the algorithm, consider the example adapted from
Mervin's work with Wagner and others in the same area
\cite{mervin_variance_2012} and presented in
Figure~\ref{fig:msod_example}.
\begin{figure}[h!]
  \begin{center}
    \scalebox{0.8}{ \input{msod_example.pdftex_t} }
  \end{center}
  \caption{\textbf{Overlapping domain example illustrating how domain
      overlap can reduce communication costs.}
    \textit{All particles start in the blue region of interest. The
      dashed line represents 0.5 domain overlap between domains.}}
  \label{fig:msod_example}
\end{figure}
In this example, 3 particle histories are presented emanating from the
blue region of interest. Starting with particle A, if no domain
overlap is used then the only the blue domain exists on the starting
processor. Particle A is then transported through 3 other domains
before the history ends, therefore requiring three communications to
occur in Brunner's algorithm. If a 0.5 domain overlap is permitted as
shown by the dashed line, then the starting process owns enough of the
domain such that no communications must occur in order to complete the
particle A transport process. Using 0.5 domain overlap also easily
eliminates cases such as that represented by the path of particle
C. In this case, particle C is scattering between two adjacent
domains, incurring a large latency cost for a single
particle. Finally, with particle B we observe that 0.5 domain overlap
will still not eliminate all communications. However, if 1 domain
overlap were used, the entire geometry shown in
Figure~\ref{fig:msod_example} would be contained on the source
processor and therefore transport of all 3 particles without
communication would occur.

\subsection{Parallel MCSA Algorithm}
We utilize parallel matrix-vector multiply, vector update, and vector
norm operations as outlined in \cite{saad_iterative_2003} for a
parallel MCSA implementation with these computations required in
Eqs~(\ref{eq:mcsa_1}), (\ref{eq:mcsa_2}), (\ref{eq:mcsa_4}), and
(\ref{eq:mcsa_5}). In the first step, a parallel vector update is used
to apply the residual to the previous iterate's solution in a
Richardson iteration. In the next step and Eq~(\ref{eq:mcsa_5}), the
residual is computed by a parallel matrix-vector multiply and vector
update. Once the correction is computed with a parallel adjoint
Neumann-Ulam solve, this correction is applied to the solution with a
parallel vector update. Additionally, as given by
Eq~(\ref{eq:mcsa_stopping_criteria}), 2 parallel vector reductions
will be required to check the stopping criteria: one initially to
compute the infinity norm of the source vector, and another at every
iteration to compute the infinity norm of the residual vector.

To parallelize the solution of Eq~(\ref{eq:mcsa_3}), we apply the
MSOD Neumann-Ulam algorithm presented in the previous section. The
problem is potentially replicated with overlap and the Monte Carlo
procedure returns a correction vector, $\delta \mathbf{x}$, with the same
parallel decomposition as the input linear problem. As was the case
for generating the replications required for a multiple set
implementation, the explicit matrix and vector operations required for
the rest of an MCSA iteration occur only on the subset of processors
containing the primary set\footnote{For applications where resiliency
  is potentially of concern, the operations in Eqs~(\ref{eq:mcsa_1}),
  (\ref{eq:mcsa_2}), (\ref{eq:mcsa_4}), and (\ref{eq:mcsa_5}) may
  be replicated without significant penalty. Doing so my alleviate
  issues where any part of the linear problem or residual is disturbed
  as now there will be multiple copies of these data
  structures.}. Only the Monte Carlo data structures exist on the rest
of the processors in the problem as replication of the other
operations does not generate any more information that could be used
to accelerate the time to solution.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Parallel Scaling Studies}
We will next measure performance in various scaling studies using an
implementation of the parallel MCSA algorithm to assess its quality
using a simple two-dimensional neutron diffusion problem in a
homogeneous medium. For the scaling results presented here, all
parallel MCSA results were computed using the Monte Carlo Linear
Solvers\footnote{MCLS is an open source C++ library built on the
  Trilinos\cite{heroux_overview_2005} framework and can be downloaded
  at \url{https://github.com/sslattery/MCLS}} (MCLS) library generated
specifically for this work. For every scaling study presented, the
calculations were performed 3 times with the average values reported
for wall time and those average values used for the efficiency
computations.

>>>>

where $W_c$ is a user-defined cutoff value. The random walk will then
be terminated after $m$ steps if $W_m < W_f$.

@@

The \textit{Fixed-Point Monte Carlo Synthetic Acceleration} method is
defined as:
\begin{subequations}
  \begin{gather}
    \label{eq:mcsa_1}
    \mathbf{r}^{k} = \mathbf{b} - \mathbf{A}\mathbf{x}^{k}\:,\\
    \label{eq:mcsa_2}
    \mathbf{x}^{k+1/2} = \mathbf{x}^k + \mathbf{r}^k\:,\\
    \label{eq:mcsa_3}
    \mathbf{r}^{k+1/2} = \mathbf{b} - \mathbf{A}\mathbf{x}^{k+1/2}\:,\\
    \label{eq:mcsa_4}
    \mathbf{A}\delta\mathbf{x}^{k+1/2} = \mathbf{r}^{k+1/2}\:,\\
    \label{eq:mcsa_5}
    \mathbf{x}^{k+1} = \mathbf{x}^{k+1/2} + \delta \mathbf{x}^{k+1/2}\:,
  \end{gather}
  \label{eq:mcsa}
\end{subequations}
where $\mathbf{r}$ is the residual vector, $\delta\mathbf{x}$ is the
Monte Carlo correction vector, and $k$ indicates the iteration
index. Here, a Neumann-Ulam Monte Carlo method is used to generate the
solution correction in Eq~(\ref{eq:mcsa_4}) using the residual as
source and Richardson's iteration in Eq~(\ref{eq:mcsa_2}) has been
rewritten as a residual correction. Using Monte Carlo in this way
achieves the same effect as Halton's method, decoupling its
convergence rate from the overall convergence rate of the method. For
the Neumann-Ulam method, a set number of random walk permutations is
specified to generate the correction at each MCSA iteration. Adding
more histories to the Neumann-Ulam sequence reduces the statistical
uncertainty in $\delta\mathbf{x}$ and further accelerates the
fixed-point iteration. In addition to the Monte Carlo solver
parameters dictating the number of histories and weight cutoff, the
outer MCSA iterations also have the following stopping criteria:
\begin{equation}
  ||\mathbf{r}||_\infty < \epsilon \ ||\mathbf{b}||_\infty\:,
  \label{eq:mcsa_stopping_criteria}
\end{equation}
where $\epsilon$ is a user-defined tolerance.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Parallel Algorithms}
In this section we devise a parallel algorithm for the Neumann-Ulam
Monte Carlo method based on the multiple-set overlapping-domain
decomposition algorithm and a parallel algorithm for the MCSA
iteration that leverages the parallel Monte Carlo algorithm and
general parallel matrix-vector operations.

\subsection{Parallel Neumann-Ulam Algorithm}
In the literature, current implementations of parallel Neumann-Ulam
methods have been limited to full domain replication with parallelism
exploited through individual histories
\cite{alexandrov_efficient_1998}. For high performance computing
environments, domain decomposition strategies have been identified as
important for Monte Carlo applications
\cite{brunner_comparison_2006,siegel_analysis_2012}. In a domain
decomposed Monte Carlo implementation, stochastic histories must be
communicated between adjacent domains and the owning compute nodes as
the simulation progresses and they transition to locations outside of
the local domain.

In the context of radiation transport, in 2009 Brunner and Brantley
provided a fully asynchronous domain decomposed parallel algorithm as
implemented in production implicit Monte Carlo codes
\cite{brunner_efficient_2009}. In their algorithm, a set of mutually
exclusive tasks enabled by the fully asynchronous communication
patterns are executed. For the Neumann-Ulam method, mutually
exclusivity permits all local operations to occur independently of
other processes in the system to achieve an optimal overlap of work
and communication. We will adapt their algorithm and directly apply it
to construct a parallel formulation of the Neumann-Ulam method. Direct
analogs can be derived from their work by noting that the primary
difference between solving a linear system with a Neumann-Ulam method
and traditional fixed source Monte Carlo transport problems is the
content of the Markov chains that are generated.

Consider their communication pattern for the 9 subdomain example given
by Figure~\ref{fig:nearest_neighbor_comm}. In this pattern, each
boundary domain has two neighbors and the center domain four neighbors
with which they will communicate parallel histories. For each set of
neighbors, a non-blocking send and receive is initiated and data
buffers allocated with a user-defined size for incoming and outgoing
histories. This non-blocking structure is critical to the performance
of the algorithm in that it permits local history transport to
continue while new histories to transport are being collected in the
buffers. When a given process is ready to do more work, it can check
these data buffers for incoming histories requiring further
transport.

@@

Given the mutual exclusivity of the transport algorithm, an additional
communcation sequence is required to efficiently stop the algorithm
after all histories have been computed. To stop transport, Brunner and
Brantley use an asynchronous binary communication tree as presented
for the same 9 subdomain example in
Figure~\ref{fig:binary_comm_tree}. In this communication pattern, each
process has one parent process (except for process 0) to which it will
non-blocking send the number of histories that terminated their
transport procedure by weight cutoff in the local
domain. Equivalently, each process has up to two child processes from
which it will receive their completed number of histories with a
non-blocking receive operation. Setting up a tree in this manner lets
the completed history tally be updated incrementally and funneled to
the root process in a mutually exclusive manner. Once the root process
has tallied a completed number of histories equal to the number of
histories in the source, transport is complete. Once this occurs, the
root process non-blocking sends the stop message to its children and
each child process non-blocking receives a stop message from the root
as shown in Figure~\ref{fig:binary_comm_tree}. The stop message is
then propagated up the tree in the same manner between parents and
children.
\begin{figure}[h!]
  \begin{center}
    \scalebox{0.6}{
      \input{binary_comm_tree.pdftex_t} }
  \end{center}
  \caption{Binary communication tree for coordinating the end of a
    parallel Neumann-Ulam solve. \textit{Each child process reports to
      its parents how many histories completed within its domain. When
      the root process sums all complete histories, it forwards the
      stop signal to its children which in turn forward the message up
      the tree. The subdomains are indexed by an integer.}}
  \label{fig:binary_comm_tree}
\end{figure}

\subsection{MSOD Algorithm}
At the 2010 SNA+MC meeting, Wagner and colleagues presented the
\textit{multiple-set overlapping-domain} (MSOD) decomposition method
for parallel Monte Carlo applications for full-core light water
reactor analysis \cite{wagner_hybrid_2010}. In their work, overlap
between adjacent domains in the decomposition was used to decrease the
number of particles leaving the local domain. In addition, Wagner
utilized a level of replication such that the decomposition was only
generated on $O(100)$ processors and if replicated $O(1,000)$ times
achieves simulation on $O(100,000)$ processors, thus providing spatial
and particle parallelism. Each collection of processors that
constitutes a representation of the entire domain is referred to as a
set, and within a set overlap occurs among its sub-domains.

To demonstrate the algorithm, consider the example presented in
Figure~\ref{fig:msod_example} adapted from Mervin's work with Wagner
and others in the same area \cite{mervin_variance_2012}.
\begin{figure}[h!]
  \begin{center}
    \scalebox{0.8}{ \input{msod_example.pdftex_t} }
  \end{center}
  \caption{\textbf{Overlapping domain example illustrating how domain
      overlap can reduce communication costs.}
    \textit{All particles start in the blue region of interest. The
      dashed line represents 0.5 domain overlap between domains.}}
  \label{fig:msod_example}
\end{figure}
In this example, 3 particle histories are presented emanating from the
blue region of interest. Starting with particle A, if no domain
overlap is used then the only the blue domain exists on the starting
processor. Particle A is then transported through 3 other domains
before the history ends, therefore requiring three communications to
occur in Brunner's algorithm. If a 0.5 domain overlap is permitted as
shown by the dashed line, then the starting process owns enough of the
domain such that no communications must occur in order to complete the
particle A transport process. Using 0.5 domain overlap also easily
eliminates cases such as that represented by the path of particle
C. In this case, particle C is scattering between two adjacent
domains, incurring a large latency cost for a single
particle. Finally, with particle B we observe that 0.5 domain overlap
will still not eliminate all communications. However, if 1 domain
overlap were used, the entire geometry shown in
Figure~\ref{fig:msod_example} would be contained on the source
processor and therefore transport of all 3 particles without
communication would occur.

\subsection{Parallel MCSA Algorithm}
We utilize parallel matrix-vector multiply, vector update, and vector
norm operations as outlined in \cite{saad_iterative_2003} for a
parallel MCSA implementation with these computations required in
Eqs~(\ref{eq:mcsa_1}), (\ref{eq:mcsa_2}), (\ref{eq:mcsa_3}), and
(\ref{eq:mcsa_4}). In Eqs~(\ref{eq:mcsa_1}) and (\ref{eq:mcsa_3}), the
residual is computed by a parallel matrix-vector multiply and vector
update. In Eq~(\ref{eq:mcsa_2}) a parallel vector update is used to
apply the residual to the previous iterate's solution in a Richardson
iteration. Once the correction is computed with a parallel adjoint
Neumann-Ulam solve, this correction is applied to the solution with a
parallel vector update in Eq~(\ref{eq:mcsa_5}). Additionally, as given
by Eq~(\ref{eq:mcsa_stopping_criteria}), 2 parallel vector norm
operations will be required to check the stopping criteria: one
initially to compute the infinity norm of the source vector, and
another at every iteration to compute the infinity norm of the
residual vector.

To parallelize the solution of Eq~(\ref{eq:mcsa_4}), we apply the MSOD
Neumann-Ulam algorithm presented in the previous section. The problem
potentially has both replication and overlap and the Monte Carlo
procedure returns the correction vector, $\delta \mathbf{x}$, with the
same parallel decomposition as the input linear problem. Although
replication of the Monte Carlo problem is required for a multiple set
implementation, the explicit matrix and vector operations required for
the rest of an MCSA iteration occur only on the subset of processors
containing the description of the linear problem\footnote{For
  applications where resiliency is potentially of concern, the linear
  problem and subsequently the operations in Eqs~(\ref{eq:mcsa_1}),
  (\ref{eq:mcsa_2}), (\ref{eq:mcsa_4}), and (\ref{eq:mcsa_5}) may be
  replicated with the penalty of broadcasting the data. Doing so may
  alleviate issues where any part of the linear problem or residual is
  disturbed as now there will be multiple copies of these data
  structures.}. Only the Monte Carlo data structures exist on the rest
of the processors in the problem as replication of the other
operations does not generate any more information that could be used
to accelerate the time to solution.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Parallel Scaling Studies}
We will next measure performance of the parallel MCSA algorithm in
various scaling studies to assess its quality using a simple
two-dimensional neutron diffusion problem in a homogeneous medium. For
the scaling results presented here, all parallel MCSA results were
computed using the Monte Carlo Linear Solvers\footnote{MCLS is an open
  source C++ library built on the Trilinos\cite{heroux_overview_2005}
  framework and can be downloaded at
  \url{https://github.com/sslattery/MCLS}} (MCLS) library generated
specifically for this work. For every scaling study presented, the
calculations were performed 3 times with the average values reported
for wall time and those average values used for the efficiency
computations.
